Stack Safety is a Security Property

### 2021-04-12 tex/main.tex
pass on abstract

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
\apt{maybe: ``Stack safety is a testable security property''?}\bcp{That
  would sacrifice a lot of oomph for a little bit of precision, IMO.  Prefer
  to leave it out of the title but hit it strongly in the abstract.}%
What is stack safety? The phrase is associated with a variety of compiler,
run-time, and hardware mechanisms for guarding against corruption of stack
memory.  But these mechanisms mostly lack rigorous specifications, appealing
either to intuitive expectations of how good stack-using programs should
behave or to specific examples of bad behavior.

We propose a formal criterion for stack safety, phrased in terms of
language-based security: a combination of an integrity property (``each
caller's stack frame is invariant by the callee'') and a confidentiality
property (``the callee's behavior is insensitive to differences in the
caller's state''). These properties are sensible even in the presence of
abnormal control flow. We further apply a straightforward notion of
``well-bracketed control flow'' that restricts control flow to the
typical pattern matched calls and returns.

We show that our properties describe the behavior the stack-safety
``micro-policies'' of~\citet{DBLP:conf/sp/RoesslerD18}
using property-based randomized testing. An eager micropolicy
that catches violations immediately enforces our primary ``stepwise''
properties, and we define weaker, more extensional ``observational''
properties that are enforced even by a ``lazy'' micropolicy -- one
that, for performance reasons, may catch violations after they occur
but before they become visible.

We argue that our properties are suited to a range of other enforcement
mechanisms. The strict stepwise properties can describe mechanisms
that catch errors immediately, as is typical. While the observational
properties are closely linked to lazy micropolicies they are weak enough
to be a lower bound that captures stack safety for any reasonable enforcement.

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
%\apt{maybe: ``Stack safety is a testable security property''?}\bcp{That
%  would sacrifice a lot of oomph for a little bit of precision, IMO.  Prefer
%  to leave it out of the title but hit it strongly in the abstract.}%
What is stack safety? The phrase is associated with a variety of compiler,
run-time, and hardware mechanisms for guarding against corruption of stack
memory.  But these mechanisms typically lack rigorous specifications;
they rely instead on informal descriptions of
the safe stack manipulation behaviors that they allow,
or specific examples of the bad behaviors that they prevent.

We propose a formal criterion \apt{criteria?} for stack safety, phrased in terms of
language-based security: a combination of an integrity property (``each
caller's stack frame is held invariant by the callee'') and a confidentiality
property (``the callee's behavior is insensitive to differences in the
caller's state''). These properties are sensible even in the presence of
abnormal control flow.\apt{Is this important enough to mention here?}
We further apply\apt{what does this mean? we didn't
  invent it} a straightforward notion of
``well-bracketed control flow'' that restricts control flow to the
typical pattern of matched calls and returns.

We show that our properties describe the behavior of the stack-safety
``micro-policies'' of~\citet{DBLP:conf/sp/RoesslerD18}
using property-based randomized testing. An eager micro-policy
that catches violations immediately enforces our primary ``stepwise''
properties, and we define weaker, more extensional ``observational''
properties that are enforced even by a ``lazy'' micro-policy -- one
that, for performance reasons, may catch violations after they occur
but before they become visible.

We argue \apt{do we?} that our properties are suited to a range of other enforcement
mechanisms. The strict stepwise properties can describe mechanisms
that catch errors immediately, as is typical. While the observational
properties are closely linked to lazy micro-policies they are weak enough
to be a lower bound that captures stack safety for any reasonable enforcement mechanism.

\apt{This is a good story, but does it describe the paper we are able to produce this week?
  We were rejected before exactly because we claimed to have
  a general criterion, but did not in fact demonstrate its generality (which is not
  obvious). What has changed?}
